Next Trippy Structures\thanks{Supported by organization x.}

### 2018-12-13 paper.tex
Hard part "done"

\newcommand{\acumm}{T-Matrices} % T is for Tirso!
\newcommand{\ctr}{NewCTR (name subject to change)}

@@

@@

\begin{algorithm}[H]
\SetKwData{la}{l$_a$}\SetKwData{lz}{l$_z$}\SetKwData{sa}{s$_a$}\SetKwData{sz}{s$_z$}\SetKwData{ta}{t$_a$}\SetKwData{tz}{t$_z$}\SetKwData{pattern}{pattern}\SetKwData{left}{left}\SetKwData{right}{right}\SetKwData{csa}{CSA}\SetKwData{wmj}{WMJ}\SetKwData{leftzero}{left$_0$}\SetKwData{rightzero}{right$_0$}\SetKwData{a}{a}\SetKwData{z}{z}\SetKwData{ja}{j$_a$}\SetKwData{jz}{j$_z$}\SetKwData{n}{n}\SetKwData{ap}{a'}\SetKwData{zp}{z'}\SetKwData{offset}{offset}
 \SetKwFunction{GetRange}{GetRange}\SetKwFunction{GetJCodes}{GetJCodes}\SetKwFunction{GetCount}{GetCount}\SetKwFunction{GetPsi}{$\Psi$}\SetKwFunction{GetRangeSpecial}{GetRange$^*$}\SetKwFunction{wml}{WML}\SetKwFunction{TrackUp}{TrackUp}\SetKwFunction{Select}{Select}
 \KwData{\la,\lz,\sa,\sz, times \ta,\tz and length of the sequence \n}
 \KwResult{Number of occurences}
 \BlankLine
 \pattern $\leftarrow \{\sz,0,\sa\}$\;
 \left,\right $\leftarrow$ \GetRange{\csa, $0$, \n, \pattern}\;
 \leftzero $\leftarrow$ \GetPsi{\csa, \left}\;
 \rightzero $\leftarrow$ \GetPsi{\csa, \right}\;
 \tcp{\right-\left = \rightzero-\leftzero}
 \a,\z $\leftarrow$ \GetRange{\wml{0},\leftzero,\rightzero,\la}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\la,\sa,\ta,\tz}\;
 \a,\z $\leftarrow$ \GetRangeSpecial{\wmj,\a,\z,\ja,\jz}\;
 \ap $\leftarrow$ \TrackUp{\wml{0},\a}\;
 \zp $\leftarrow$ \TrackUp{\wml{0},\z}\;
 \tcp{\z-\a = \zp-\ap}
 \offset $\leftarrow$ \Select{\csa,\sz}\;
 \a,\z $\leftarrow$ \GetRange{\wml{\sz},\left-\offset~$+$~\ap-\leftzero,
 \left-\offset~$+$~\ap-\leftzero,\lz}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\lz,\sz,\ta,\tz}\;
 \Return{\GetCount{\wmj,\offset~+~\a,\offset~+~\z,\ja,\jz}}\;

 \caption{Querying for all features on \ctr}
\end{algorithm}

>>>>

\newcommand{\acumm}{T-Matrices} % T is for Tirso!
\newcommand{\ctr}{NewCTR (name subject to change)\ }

@@

\begin{algorithm}[H]
\SetKwData{l}{$l$}\SetKwData{lz}{l$_z$}\SetKwData{s}{s}\SetKwData{sz}{s$_z$}\SetKwData{ta}{t$_a$}\SetKwData{tz}{t$_z$}\SetKwData{pattern}{pattern}\SetKwData{left}{left}\SetKwData{right}{right}\SetKwData{csa}{CSA}\SetKwData{wmj}{WMJ}\SetKwData{leftzero}{left$_0$}\SetKwData{rightzero}{right$_0$}\SetKwData{i}{i}\SetKwData{z}{z}\SetKwData{ja}{j$_a$}\SetKwData{jz}{j$_z$}\SetKwData{n}{n}\SetKwData{ap}{a'}\SetKwData{zp}{z'}\SetKwData{offset}{offset}
 \SetKwFunction{GetBounds}{GetBounds}\SetKwFunction{GetJCodes}{GetJCodes}\SetKwFunction{GetCount}{GetCount}\SetKwFunction{GetPsi}{$\Psi$}\SetKwFunction{GetRangeSpecial}{GetRange$^*$}\SetKwFunction{bsearch}{binary\_search}\SetKwFunction{lbound}{lower\_bound}\SetKwFunction{ubound}{upper\_bound}
 \SetKwProg{Fn}{Function}{\string:}{}

 \Fn{\GetJCodes{\l,\s,\ta,\tz}}{
 \KwData{line \l, stop \s, times \ta,\tz}
 \KwResult{jcodes for \ta and \tz}
 \BlankLine
 \offset $\leftarrow$ $avgTime_{\l}(\bsearch{$lineStop_\l$, \s})$\;
 \Return{\lbound{$initialTime_\l$, \ta-\offset}, \ubound{$initialTime_\l$, \tz-\offset}}\;
 }

 \caption{Obtaining the codes of the journeys from the line \l that should arrive to the stop \s within the time range given by \ta and \tz}
\end{algorithm}

@@

\begin{algorithm}[H]
\SetKwData{la}{$l_a$}\SetKwData{lz}{$l_z$}\SetKwData{sa}{s$_a$}\SetKwData{sz}{s$_z$}\SetKwData{ta}{t$_a$}\SetKwData{tz}{t$_z$}\SetKwData{pattern}{pattern}\SetKwData{left}{left}\SetKwData{right}{right}\SetKwData{csa}{CSA}\SetKwData{wmj}{WMJ}\SetKwData{leftzero}{left$_0$}\SetKwData{rightzero}{right$_0$}\SetKwData{a}{a}\SetKwData{z}{z}\SetKwData{ja}{j$_a$}\SetKwData{jz}{j$_z$}\SetKwData{n}{n}\SetKwData{ap}{a'}\SetKwData{zp}{z'}\SetKwData{offset}{offset}
 \SetKwFunction{GetRange}{GetRange}\SetKwFunction{GetJCodes}{GetJCodes}\SetKwFunction{GetCount}{GetCount}\SetKwFunction{GetPsi}{$\Psi$}\SetKwFunction{GetRangeSpecial}{GetRange$^*$}\SetKwFunction{wml}{WML}\SetKwFunction{TrackUp}{TrackUp}\SetKwFunction{Select}{Select}\SetKwFunction{fxy}{FromXtoY\_full}
 \SetKwProg{Fn}{Function}{\string:}{}

 \Fn{\fxy{\la,\lz,\sa,\sz,\ta,\tz,\n}}{
 \KwData{lines \la,\lz, stops \sa,\sz, times \ta,\tz and length of the sequence \n}
 \KwResult{Number of occurences}
 \BlankLine
 \pattern $\leftarrow \{\sz,0,\sa\}$\;
 \left,\right $\leftarrow$ \GetRange{\csa, $0$, \n, \pattern}\;
 \leftzero $\leftarrow$ \GetPsi{\csa, \left}\;
 \rightzero $\leftarrow$ \GetPsi{\csa, \right}\;
 \tcp{\right-\left = \rightzero-\leftzero}
 \a,\z $\leftarrow$ \GetRange{\wml{$0$},\leftzero,\rightzero,\la}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\la,\sa,\ta,\tz}\;
 \a,\z $\leftarrow$ \GetRangeSpecial{\wmj,\a,\z,\ja,\jz}\;
 \ap $\leftarrow$ \TrackUp{\wml{$0$},\a}\;
 \zp $\leftarrow$ \TrackUp{\wml{$0$},\z}\;
 \tcp{\z-\a = \zp-\ap}
 \offset $\leftarrow$ \Select{\csa,\sz}\;
 \a,\z $\leftarrow$ \GetRange{\wml{\sz},\left-\offset~$+$~\ap-\leftzero,
 \left-\offset~$+$~\ap-\leftzero,\lz}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\lz,\sz,\ta,\tz}\;
 \Return{\GetCount{\wmj,\offset~+~\a,\offset~+~\z,\ja,\jz}}\;
 }

 \caption{Querying for all features on \ctr where \DataSty{CSA}, \DataSty{WML} and \DataSty{WMJ} are structures (i), (ii) and (iii), respectively}
\end{algorithm}
